```{r  include = FALSE}
library(tidyverse)
library(papaja)
library(here)
source(here('scripts','helpers.R'))
source(here('scripts','krippendorff_alpha.R'))
source(here('scripts','load_data.R'))
```

```{r demographics, echo=FALSE}
COLNAMES = c('', 'OCD','TICSA', 'online', 'wet')

demographics_df = data.frame(
  X1 = c('N', 'Female N', 'Mean age (SD)', 'Anxiety Measure', 'Anxiety Score (SD)'),
  X2 = c(ocd.N, format_count_percentage(ocd.femaleN, ocd.N),  format_mean_sd(ocd.age.mean, ocd.age.sd), 'OCI-R', format_mean_sd(ocd.ocir.mean, ocd.ocir.sd)),
  X3 = c(sticsa.N, format_count_percentage(sticsa.femaleN, sticsa.N), format_mean_sd(sticsa.age.mean, sticsa.age.sd), 'TICSA', format_mean_sd(sticsa.sticsa.mean,sticsa.sticsa.sd)),
  X4 = c(online.N, '--', '--', 'TICSA', format_mean_sd(online.sticsa.mean,online.sticsa.sd)),
  X5 = c(wet.N, format_count_percentage(wet.femaleN, wet.N), format_mean_sd(wet.age.mean, wet.age.sd), 'OASIS', format_mean_sd(wet.oasis.mean,wet.oasis.sd))
)

demographics_df %>%
  apa_table(
    caption = 'Demographics',
    col.names = COLNAMES,
    col_spanners = list( "Interview" = 2:3, "Self-administered" = 4:5)
  )
```

## Methods: Experiment 1

Experiment 1 aimed to evaluate the feasibility and potential utility of the face to face CTSI for identifying core threats among individuals exhibiting high levels of obsessive-compulsive (OC) symptoms.

### Participants

Participants from a pre-existing database of individuals who had previously agreed to participate in research studies and had completed the OCI-R were contacted
by a research assistant and provided informed consent to participate in the current study.
Demographic details can be found in Table \@ref(tab:demographics).
A median OCI-R score of `r ocd.ocir.median` indicates that most participants were well within the severe range of symptoms [@abramovitchSeverityBenchmarksContemporary2020]. 
Additionally, `r ocd.diamondN`  (`r apa_percentage(ocd.diamondN/ocd.N)`) participants met the criteria for OCD according to the OCD section of the DIAMOND interview.
Full demographic details can found in Table\ \@ref(tab:demographics).

### Procedure

Participants completed a set of questionnaires and underwent a zoom interview lasting between 45 minutes to two hours.
The interview included the OCD section of the DIAMOND and the CTSI.
The CTSI was used to identify core threats underlying two compulsions (proximal threats).
When possible, the compulsions were chosen to be as dissimilar as possible (e.g. a cleaning compulsion and a checking compulsion).
The interview focused on what the participants felt would happen if they did not perform their ritualistic behaviors.
Compensation was provided at a rate of approximately \$10 per hour or in the form of course credit.

### Measures

The face to face CTSI was used to identify proximal and core threats, as discussed above.
Three judges scored each threat but did *not* achieve sufficient reliability.
Subsequent analyses use a consensus score.
The data from this study were used to improve training so that the judges reached reliability in later experiments.
Thus, despite the initially poor reliability score, we argue that the consensus score is valid.

**Obsessive Compulsive Inventory Revised [OCIR\; @foaObsessiveCompulsiveInventoryDevelopment2002]**: The OCIR is a self-report measure consisting of 18 Likert-scale items ranging from 0 to 4, which assess the distress associated with specific OCD symptoms.
It has demonstrated robust psychometric properties in both clinical and student populations [@huppertOCIRValidationSubscales2007; @foaObsessiveCompulsiveInventoryDevelopment2002].
With an omega coefficient of `r ocd.ocir.omega`, the OCIR has shown high internal consistency and is a reliable measure of OCD symptom severity.

**Diagnostic Interview for Anxiety, Mood, and OCD and Related Neuropsychiatric Disorders [DIAMOND\; @tolinPsychometricPropertiesStructured2018]**: The DIAMOND is a semi-structured diagnostic interview designed to diagnose DSM-5 psychiatric disorders, with robust psychometric properties.
In this study, only the OCD section of the DIAMOND was administered to establish OCD diagnoses.
The DIAMOND has shown excellent inter-rater reliability, test-retest reliability, and both convergent and divergent validity [@tolinPsychometricPropertiesStructured2018].

## Methods: Experiment 2

Experiment 2 aimed to extend Experiment 1 by focusing on a transdiagnostic anxious population.
Furthermore, it aimed to investigate both test retest reliability and inter-rater reliability.

### Participants

Participants were sourced from a pre-existing database of individuals who had previously agreed to participate in research studies and had completed TICSA.
Each participant was contacted by a research assistant and provided informed consent to participate in the study.
Full demographic details can found in Table \@ref(tab:demographics).

### Procedure

Participants initially completed the CTSI with one interviewer via Zoom, with interviews lasting between 30 and 90 minutes.
The interview focused on the fear that participants found most impactful.
Approximately one to two months later (Median = `r sticsa.days.median` days; Range: `r sticsa.days.min`–`r sticsa.days.max` days), they completed the CTSI again, focusing on the same proximal threat but with a different interviewer.
A total of `r sticsa.dropoutN` participants (`r apa_percentage(sticsa.dropoutN/sticsa.N)`) dropped out between sessions.
Compensation was provided at a rate of approximately \$10 per hour or in the form of course credit.

### Measures

```{r include=FALSE}
raw.judges.sticsa = rbind(
  read_csv(here('data','CTSI.coding.sticsa.baraa.csv')) %>% mutate(id=1) %>% mutate(across(.cols = Affiliation:`No Idea`, ~str_replace_all(.x, "לא", NA_character_))),
  read_csv(here('data','CTSI.coding.sticsa.tomer.csv')) %>% mutate(id=2),
  read_csv(here('data','CTSI.coding.sticsa.yuval.csv')) %>% mutate(id=3)
) %>%
  filter(is.na(`No Idea`)) %>% # treat "no idea" as missing data
  filter(!if_all(Affiliation:`No Idea`, is.na)) # remove rows with no answer

jid = raw.judges.sticsa$id
uid = raw.judges.sticsa$rid %>% as.factor()
values = raw.judges.sticsa %>% select(-id, -rid) %>%as.matrix %>% apply(1,function(i){which(!is.na(i))})
sticsa.krip = krippendorff(jid = jid, uid = uid, values = values, agree = agree_fn)
```

The face-to-face CTSI was used to identify proximal and core threats, as discussed above.
Three judges scored each threat and achieved good inter-rater reliability (Krippendorff's $\alpha$ = `r sticsa.krip`).

**The Trait Inventory for Cognitive and Somatic Anxiety [TICSA\; @reeDistinguishingCognitiveSomatic2008]** was used as a 21-item self-report measure to assess cognitive and somatic symptoms of trait anxiety.
Each item on the TICSA is rated on a 4-point Likert scale ranging from 0 (not at all) to 3 (very much so), with higher scores indicating greater severity of anxiety symptoms.
The TICSA has demonstrated reliability and validity in measuring trait anxiety in prior research [@reeDistinguishingCognitiveSomatic2008; @grosPsychometricPropertiesStateTrait2007].
In this experiment, the TICSA showed high internal consistency, with an omega coefficient of `r sticsa.sticsa.omega`.

## Methods: Experiment 3

Experiment 3 aimed to extend Experiment 2 by utilizing a self-administered version of the CTSI.

### Participants and Procedure

Participants were sourced from a pre-existing database of individuals who had previously agreed to participate in research studies and had completed TICSA.
Each participant was contacted by a research assistant and provided informed consent to participate in the study.
Due to a technical error, the age and gender of participants were not recorded; however, the sampling procedure was similar to Experiment 2, suggesting similar demographics.
Full demographic details can found in Table\ \@ref(tab:demographics).
Participants were sent a link to complete the self-administered CTSI and several relevant questionnaires.
Participants were compensated for their time at approximately \$10 per hour or received course credit where applicable.

### Measures

```{r include=FALSE}
raw.judges.online = rbind(
  read_csv(here('data','CTSI.coding.online.baraa.csv')) %>% mutate(id=1) %>% mutate(across(.cols = Affiliation:`No Idea`, ~str_replace_all(.x, "לא", NA_character_))),
  read_csv(here('data','CTSI.coding.online.tomer.csv')) %>% mutate(id=2),
  read_csv(here('data','CTSI.coding.online.yuval.csv')) %>% mutate(id=3)
) %>%
  filter(is.na(`No Idea`)) %>% # treat "no idea" as missing data
  filter(!if_all(Affiliation:`No Idea`, is.na)) # remove rows with no answer

jid = raw.judges.online$id
uid = raw.judges.online$rid %>% as.factor()
values = raw.judges.online %>% select(-id, -rid) %>%as.matrix %>% apply(1,function(i){which(!is.na(i))})
online.krip = krippendorff(jid = jid, uid = uid, values = values, agree = agree_fn)
```

The self-administered CTSI was used to identify proximal and core threats, as discussed above.
Three judges scored each threat and achieved good inter-rater reliability (Krippendorff's $\alpha$ = `r online.krip`).
The TICSA was used to measure anxiety, showing high internal consistency, with an omega coefficient of `r online.sticsa.omega`.

## Experiment 4

Experiment 4 aimed to expand Experiment 3 by using an international, English speaking population.

### Participants and Procedure

Participants were sampled via the Prolific platform for online research and were paid £9 per hour for participation.
They were first screened to select high anxiety individuals.
Inclusion criteria included high pathological anxiety [ greater than 4 on the OASIS; @normanDevelopmentValidationOverall2006],
and impaired daily function [at least one item scored above 2 on the WSAS; @mundtWorkSocialAdjustment2002].
Exclusion criteria included severe depression [greater than 14 on the PHQ; @kroenkePHQ8MeasureCurrent2009], post-trauma [greater than 6 on the short PCL-5; @zuromskiDevelopingOptimalShortform2019], or psychotic symptoms [items 19 or 20 from the DIAMOND screener; @tolinPsychometricPropertiesStructured2018].
Additionally, fluency in English was required.
Participants who reported head injury or reading and writing difficulties in the Prolific system were excluded.
Only experienced users on the Prolific platform with an approval rate above 95% and a minimum of 300 previous submissions were allowed to participate in the study.
Full demographic details can be found in Table \@ref(tab:demographics).
Participants were then referred to the main experiment.
Within the experiment, they signed a consent form, completed a set of questionnaires related to a different experiment, and finally completed the self-administered CTSI.

### Measures

```{r include=FALSE}
raw.judges.wet = rbind(
  read_csv(here('data','CTSI.coding.wet.baraa.csv')) %>% mutate(id=1),
  read_csv(here('data','CTSI.coding.wet.tomer.csv')) %>% mutate(id=2),
  read_csv(here('data','CTSI.coding.wet.yuval.csv')) %>% mutate(id=3)
) %>%
  filter(rid != 'rid') %>% # remove double header
  filter(is.na(`No Idea`)) %>% # treat "no idea" as missing data
  filter(!if_all(Affiliation:`No Idea`, is.na)) # remove rows with no answer

jid = raw.judges.wet$id
uid = raw.judges.wet$rid %>% as.factor()
values = raw.judges.wet %>% select(-id, -rid) %>%as.matrix %>% apply(1,function(i){which(!is.na(i))})
wet.krip = krippendorff(jid = jid, uid = uid, values = values, agree = agree_fn)
```

The self-administered CTSI was used to identify proximal and core threats, as discussed above.
Three judges scored each threat and achieved good inter-rater reliability (Krippendorff's $\alpha$ = `r wet.krip`).

**The Overall Anxiety Severity and Impairment Scale [OASIS; @normanDevelopmentValidationOverall2006]** was used to measure anxiety.
The OASIS assesses the frequency, intensity, and functional impairment of anxiety and fear over the past week.
Participants rate their anxiety on a 5-point scale from 0 (Little or None) to 4 (Extreme or All the Time).
Higher scores indicate more severe anxiety-related impairment, with a cut-off score of eight recommended for distinguishing anxiety disorders and a change of four points considered clinically significant [@moorePsychometricEvaluationOverall2015].
The OASIS has strong psychometric properties, with an omega coefficient of `r wet.oasis.omega` in our sample, indicating high reliability [@normanDevelopmentValidationOverall2006].
