# Results

```{r  include = FALSE}
source(here('scripts','simpsonD.R'))
source(here('scripts','agreement.analysis.R'))
# Setup agreement statistics 

# Define the path to the agreement RDS file
agreementRdsFile = here('docs', 'manual_cache', 'agreement.rds')

# Create the directory if it does not exist
dir.create(here('docs', 'manual_cache'), recursive = TRUE, showWarnings = FALSE)

R = 1e4 # bootstrap repetitions, this takes a while thus the cache... 
# uncache: file.remove(agreementRdsFile)
# Check if the RDS file exists
if (file.exists(agreementRdsFile)) {
  # If it exists, read the RDS file
  agreementLists = readRDS(agreementRdsFile)
} else {
  # If it does not exist, create the agreement lists and save them to the RDS file
  # possibly parallelize ??
  agreementLists = list(
    agreement(ocd.values %>% mutate(type = if_else(type == 'cf', 'core', 'surface')), R = R),
    agreement(sticsa.values, R = R),
    agreement(online.values, R = R),
    agreement(wet.values, R = R)
  )
  saveRDS(agreementLists, agreementRdsFile)
}
```

## The Distribution of Threat Values

The distribution of values in core and proximal threats varied across experiments, with notable differences between the face-to-face and self-administered formats (see Figure \@ref(fig:distribution)).
Proximal threats were more frequently rated as ambiguous compared to core threats. 
This discrepancy may stem from the CTSI’s emphasis on exploring values, though participants were not explicitly instructed to frame their threats in these terms. 
A more plausible explanation is that the CTSI facilitates a clearer focus on core threats during the interview process.

(ref:distribution) Distribution of threat values across experiments

```{r distribution, file=here('scripts','figure.distribution.R'), echo=FALSE, fig.cap='(ref:distribution)', warning=FALSE, cache=TRUE, out.width="90%"}
```

In the face-to-face samples, particularly in Experiment 1, distress tolerance frequently emerged as a proximal threat but was rare as a core threat.
This suggests that distress tolerance-related threats may function as mechanisms for avoiding deeper, underlying fears rather than representing the ultimate feared outcome.
Interestingly, this pattern was not observed in the self-administered versions of the CTSI, possibly because the detailed prompts in the self-administered format encouraged participants to identify harm-avoidant threats explicitly.

In the face-to-face samples, particularly in Experiment 1, distress tolerance frequently emerged as a proximal threat but was rare as a core threat.
This suggests that distress tolerance may serve as a form of avoidance rather than an ultimate feared outcome.
Because distress tolerance is often framed in broad and universally valid terms (e.g., "I can't handle this discomfort"), it allows individuals to sidestep engaging with the specific and potentially more threatening underlying fears.
In essence, focusing on distress tolerance can provide an avenue for avoidance by shifting attention away from addressing the actual threat.

Affiliation consistently appeared as a prominent value in the transdiagnostic experiments.
This could reflect an overrepresentation of socially anxious individuals in the sample, or it may indicate that the affiliation category encompasses diverse subtypes.
Differentiating between these subtypes in future research may provide greater specificity.
Alternatively, affiliation may genuinely represent the most common core threat, as suggested by theories emphasizing its evolutionary and psychological significance [cf.
@gilbertEVOLUTIONSOCIALANXIETY2001; @bowlbyAttachmentLoss1969].

## Hypothesis 1: Proximal-Core Agreement

Hypothesis 1 was that core threats represent a distinct psychological process from proximal threats.
To test this, we examined two key questions: whether core threats can be predicted based on proximal threats and whether core threats display greater diversity in content compared to proximal threats.
Across all experiments, core threats matched their corresponding proximal threats in no more than 32.5% of cases, with the lowest agreement observed in Experiment 1 (High OC sample), where the rate was 16.9%.
Among the transdiagnostic samples, agreement rates were slightly above chance.
However, after applying the Holm-Bonferroni correction for multiple comparisons [@holmSimpleSequentiallyRejective1979], only Experiment 2 (face-to-face transdiagnostic sample) demonstrated a statistically significant agreement between proximal and core threats.
These results indicate that while proximal threats may offer some information about core threats, the observed agreement rates, are clinically insufficient.
This finding supports the hypothesis that proximal threats do not reliably predict core threats, as more than 70% of core threats differed from their proximal counterparts.

The diversity of proximal threats, measured using Simpson’s $D$, ranged from 0.30 to 0.46 across experiments.
Core threats generally exhibited greater diversity than proximal threats, with the exception of Experiment 2 (face-to-face high anxiety sample), where diversity levels were equivalent.
The difference was most pronounced in Experiment 1 and 4 (face-to-face high OC, and online English speaking).
However, after correcting for multiple comparisons, only the diversity difference observed in Experiment 1 remained statistically significant.
The diversity metrics and detailed statistical results are presented in Table \@ref(tab:agreement).

```{r agreement, echo=FALSE}
rowNames = c(
  'N pairs',
  'Expected Agreement (%)',
  'Actual Agreement (%)',
  'p Agreement',
  'Proximal threats',
  'Core threats',
  'p Diversity'
)

# Initialize an empty data frame
agreement_df <- data.frame(matrix(ncol = length(agreementLists)+1, nrow = length(rowNames)))
agreement_df[,1] = rowNames

for (i in seq_along(agreementLists)){
  col = with(agreementLists[[i]], c(
    N,
    format_count_percentage(expected_count, N),
    format_count_percentage(actual_count, N),
    printp(expected_p),
    D_sf$apa_string_short,
    D_cf$apa_string_short,
    printp(D_perc_sfcf)
  ))
  agreement_df[,i+1] = col
}

agreement_df %>%
  apa_table(
    caption = 'Agreement and Diversity statistics across studies. Agreement reflects the count of expected and actual pairs of motivations aligning (p Agreement indicates the likelihood of observing this agreement by chance). Diversity is measured using the Simpson Diversity Index for proximal versus core threats (p Diversity represents the probability that core threat diversity exceeds proximal threat diversity).',
    col.names = COLNAMES,
    col_spanners = list( "Interview" = 2:3, "Self-administered" = 4:5),
    stub_indents = list( "Agreement" = 1:4, "Diversity (D)" = 5:7),
    note = 'OC - obsessive compulsive, FTF - face to face, TD - Transdiagnostic'
  )

```

After identifying core threats, participants were asked whether these threats reflected their underlying motivation for fear.
This assessment was conducted in the three trans-diagnostic samples but not in the OCD sample.
The full results are presented in Figure \@ref(fig:subjective).
Across all experiments, the majority of participants affirmed that the identified core threats accurately represented their motivation for anxiety.
Notably, the proportion of participants endorsing the core threat as their "true" motivation was consistent regardless of whether the proximal and core threats aligned or the identified core threat reflected a different motivation.
A significant proportion of participants expressed uncertainty about whether the identified core threat truly captured their underlying motivation.
However, this uncertainty was less prevalent in the self-administered versions of the CTSI, suggesting that the self-administered format may facilitate more confidence in the identification of core threats.
It is important to note that this analysis was not pre-registered and should be regarded as exploratory.
While the results are intriguing and suggest potential avenues for further investigation, they require replication and confirmation in future research.

(ref:subjective) The mosaic plot illustrates participants' responses to the question: “Does the core threat you identified reflect your true motivation?” Tile sizes represent the relative frequencies of responses across groups. The plot indicates that core threats generally align with participants’ true motivations. Sensitivity analyses confirmed that these proportions remained consistent regardless of whether core threats matched proximal threats.

```{r subjective, file=here('scripts','figure.subjective.R'), echo=FALSE, fig.cap='(ref:subjective)', warning=FALSE, cache=TRUE}
```

## Hypothesis 2: Multiple proximal threats - one core threat

```{r include=FALSE}
###################
# Within Patient Agreement
###################

# Filter data for individuals that have identified more than one core threat
d <- ocd.values %>% 
  filter(type == 'cf', is.na(`No Idea`)) %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

# Use full_join to consider all combinations of id and wave
aligned_df <- full_join(
  d %>% filter(wave == 1),
  d %>% filter(wave == 2),
  by = "id", suffix = c("_1", "_2")
) %>%
  filter(!if_all(Affiliation_1:`No Idea_1`, is.na)) %>%  # Remove rows with all NA values in wave 1
  filter(!if_all(Affiliation_2:`No Idea_2`, is.na))  # Remove rows with all NA values in wave 2

# Create lists of values for each wave
values_1 <- aligned_df %>% 
  select(Affiliation_1:`No Idea_1`) %>%
  as.matrix() %>%
  apply(1, function(i) { which(!is.na(i)) })

values_2 <- aligned_df %>% 
  select(Affiliation_2:`No Idea_2`) %>%
  as.matrix() %>%
  apply(1, function(i) { which(!is.na(i)) })

# Calculate the number of aligned rows
ocd.within.N <- nrow(aligned_df)

# Calculate overall agreement within patients
ocd.within.overall <- agree_list(values_1, values_2)

# Bootstrap to calculate agreement by chance
ocd.within.bychance.boot <- sapply(1:1e4, function(i) {
  combined <- sample(c(values_1, values_2), replace = FALSE)
  agree_list(combined[1:ocd.within.N], combined[(ocd.within.N + 1):(ocd.within.N * 2)])
})
```


## Hypothesis 2: Multiple Proximal Threats and One Core Threat

Hypothesis 2 was that one core threat often motivates multiple proximal threats.
We investigated this in Experiment 1 by administering the CTSI for two distinct compulsions (proximal threats).
Only `r format_count_percentage(ocd.within.N, ocd.N)` individuals identified core threats for both compulsions.
This limited identification often occurred because participants became fatigued and impatient by the time they were interviewed about the second compulsion.
Consequently, our data on this topic is both limited and potentially biased (e.g., is there a relationship between participants' persistence and the characteristics of their fears?).

A permutation test revealed that the median expected number of agreements was `r format_count_percentage(median(ocd.within.bychance.boot), ocd.within.N)`.
In practice, `r ocd.within.overall` (`r apa_percentage(ocd.within.overall / ocd.within.N)`, $p$ = `r printp(mean(ocd.within.bychance.boot >= ocd.within.overall))`) pairs of core threats agreed with one another.
While this result is not statistically significant, it suggests that core threats may motivate multiple proximal threats within the same individual.
Due to the small sample size, these findings should be interpreted cautiously.
Further research is warranted, as this estimate might be higher if more similar compulsions were selected.

Interestingly, some pairs might share common underlying threats, even when their coded values did not match.
For example, one woman was afraid of contamination and dying if she did not perform her cleaning compulsions (Survival) and also feared breaking up with her boyfriend, not having children, and being alone forever (Affiliation).
A deeper investigation might reveal that not having children held the same significance as not surviving for her.
This dataset, collected during the initial development of the CTSI, may have been affected by suboptimal administration.
Nonetheless, this finding underscores that the same core threats often appear to motivate different proximal threats.

## Hypothesis 3: Test Retest Validity

```{r include=FALSE}
##############################
# Within Patient Agreement
##############################

# Filter data for individuals that have identified more than one core threat
d <- sticsa.values %>% 
  filter(type == 'core', is.na(`No Idea`)) %>%
  group_by(id) %>%
  filter(n() > 1) %>%
  ungroup()

# Use full_join to consider all combinations of id and wave
aligned_df <- full_join(
  d %>% filter(wave == 1),
  d %>% filter(wave == 2),
  by = "id", suffix = c("_1", "_2")
) %>%
  filter(!if_all(Affiliation_1:`No Idea_1`, is.na)) %>%  # Remove rows with all NA values in wave 1
  filter(!if_all(Affiliation_2:`No Idea_2`, is.na))  # Remove rows with all NA values in wave 2

# Create lists of values for each wave
values_1 <- aligned_df %>% 
  select(Affiliation_1:`No Idea_1`) %>%
  as.matrix() %>%
  apply(1, function(i) { which(!is.na(i)) })

values_2 <- aligned_df %>% 
  select(Affiliation_2:`No Idea_2`) %>%
  as.matrix() %>%
  apply(1, function(i) { which(!is.na(i)) })

# Calculate the number of individuals completing both evaluations
sticsa.within.N <- nrow(aligned_df)

# Calculate overall agreement within patients
sticsa.within.overall <- agree_list(values_1, values_2)

# Bootstrap to calculate agreement by chance
sticsa.within.bychance.boot <- sapply(1:1e4, function(i) {
  combined <- sample(c(values_1, values_2), replace = FALSE)
  agree_list(combined[1:sticsa.within.N], combined[(sticsa.within.N + 1):(sticsa.within.N * 2)])
})
```

In the high-anxiety face-to-face sample, `r sticsa.within.N` individuals (`r apa_percentage(sticsa.within.N / sticsa.N)`) completed both evaluations of their core threats.
A permutation test revealed that the median expected number of agreements was `r median(sticsa.within.bychance.boot)` cases (`r apa_percentage(median(sticsa.within.bychance.boot) / sticsa.within.N)`).
In practice, `r sticsa.within.overall` pairs of core threats agreed with each other (`r apa_percentage(sticsa.within.overall / sticsa.within.N)`, $p$ = `r printp(mean(sticsa.within.bychance.boot >= sticsa.within.overall))`).

This finding suggests significant test-retest validity, indicating that the same core threats likely motivate fear over time.
Furthermore, it supports the notion that different evaluators can reliably identify the same core threat when interviewing an individual.
However, the agreement rate is slightly lower than expected.
Future research should investigate whether core threats are less stable than predicted or if adjustments to CTSI administration can improve test-retest reliability.
